# Practical 5

```{r}
pkg_vec <- c("ggplot2", "palmerpenguins", "ggthemes")
for (x in pkg_vec) {
  if (!requireNamespace(x, quietly = TRUE)) {
    install.packages(x, dependencies = TRUE)
  }
  # if you want to programmatically attach
  # libraries, this is the way to to do it
  library(x, character.only = TRUE)
}
library(ggplot2)
```

## Question 1

Simulate 100 random numbers from a normal distribution with mean 3 and standard deviation 1. Use `ggplot2` to plot the empirical density of these, and format the plot according to best practice (e.g. with axis titles, caption, etc.).

```{r}
random_numbers <- data.frame(x = 1:100, y= rnorm(100, mean = 3, sd = 1))

ggplot(data = random_numbers, aes(x = x, y=y)) +
  geom_point(aes(color = "red")) +
  labs(
    title = "Question 1",
    subtitle =  "Generated Random Numbers According To The  \nNormal Distribution Mean = 3 and Standard Deviation = 1", 
    caption = "Figure 1", 
    x = "Numbers 1 to 100",
    y = "Normally Distributed Values"
  )
  
```

Make a reference to the plot in the text (e.g. using `@fig-dens-plot`).

```{r}

```

Overlay the true density of the normal distribution on the plot (hint: use `geom_line`).

```{r}
random_numbers <- data.frame(x = 1:100, y= rnorm(100, mean = 3, sd = 1))

ggplot(data = random_numbers, aes(x = x, y=y)) +
  geom_point(aes(color = "red")) +
  geom_smooth(method ="lm") +
  labs(
    title = "Question 1",
    subtitle =  "Generated Random Numbers According To The  \nNormal Distribution Mean = 3 and Standard Deviation = 1", 
    caption = "Figure 1", 
    x = "Numbers 1 to 100",
    y = "Normally Distributed Values"
  ) +
  theme_cowplot(font_size = 15) +
  background_grid(major = "xy") +
  theme(
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white")
  )
```

------------------------------------------------------------------------

## **Question Two**

Calculate a two-way frequency table of species of penguins and island location (from the `palmerpenguins` package’s dataset), and display it according to best practices (e.g. table caption, appropriate lines, etc.).

```{r}

```
